---
title: "Getting started with R"
author: Omkar DEsai
date: today
format: html
---

### Exercise 1 {#sec-1}

* Create a vector of the letters A, B and C.

```{r}
# Your answer in code
c("A", "B", "C")
```
> Your answer as text
I created a vector using built-in function c() and added A, B and C elements

* Assign the vector to a variable `my_letters`
```{r}
# Your answer in code
my_letters <- c("A", "B", "C")
```


* Check the what happens when you run `letters` (just this) on the command line.
```{r}
# Your answer in code
letters
```

> Your answer as text
Letters is a built-in vector that contains all alphabets


* What happens when you concatenate two vectors? Add `c(my_letters , my_letters)`
```{r}
# Your answer in code
c(my_letters , my_letters)

```

> Your answer as text
When we use c() and provide to vectors in it then it gets concatenated 

* Add the number 1 to letters. What happens to the type of the vector?
```{r}
# Your answer in code
letters+1

```

> Your answer as text
Here, letters in a vector of characters and when we try to add 1 which is of numeric type hence we are getting type error

### Exercise 2


1. Create a vector `my_vec` with the numbers from 1 through 8.
2. Apply the operation `+2` to the vector/
3. Add the vector containing 1, 2, 3, 4 to `my_vec`. What do you observe?

```{r}
# Your answer in code
my_vec <- c(1:8)
my_vec+2
my_vec+c(1:4)





```



### Exercise 3

* Consider the R output of the matrix below:

```
 [,1] [,2]
 [1,]    4    1
 [2,]    9    5
 [3,]   10    7
```

1. What was one of the correct commands used to write this matrix?
2. Assign the matrix as `A`
3. Check the dimensions
4. Extract the element `5`
5. Add the vector `c(0,0,0)` as a new column and update `A`
6. Modify the element 4 to `0`
7. Compute the transpose of `A`

```{r}
# Your answer in code
matrix(data = c(4,1,9,5,10,7), nrow = 3, ncol = 2, byrow = TRUE )
A <- matrix(data = c(4,1,9,5,10,7), nrow = 3, ncol = 2, byrow = TRUE )
dim(A)
A[2:2]
A<-cbind(A,c(0,0,0))
A[1:1]<-0
t(A)



```


8. Are any values in `A` larger than 10? 
```{r}
# Your answer in code
A[A>10]
```

9. Are all values in `A` smaller than 10?
```{r}
# Your answer in code
A[A<10]
```

### Exercise 4

1. Create a function that sums up two values even if provided as characters values

```{r}
# Your answer in code
adder_fun <- function(a,b) {as.numeric(a)+as.numeric(b)}
adder_fun(10,3)
adder_fun("Omkar","Desai")


```


### Exercise 5

1. Create a function that returns the mean, median and standard deviation.

```{r}
# Your answer in code
stats_fun <- function(a) {paste("mean:",mean(a), "median:",median(a), "sd:",sd(a))}
stats_fun(c(1:10))

```


### Exercise 6
1. Create a pipe statement that counts the number of NAs in vector containing numbers, characters and missing values.
The output of `c('1' , "a", NA, "2", NA)` should be 2.

```{r}
# Your answer in code
vector<-c('1' , "a", NA, "2", NA)
sum(is.na(vector))
```


